%\documentclass[letterpaper, onecolumn, 10pt]{article}
%\linespread{2.4}
\documentclass[letterpaper, twocolumn, 10pt]{article}
\usepackage{usenix2019}
%\linespread{0.99}

\usepackage{multirow}
\usepackage{comment}
\usepackage{epsfig}
%\usepackage{kotex}
%\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{url}
\usepackage{subfig}
\usepackage{color}
\usepackage{xcolor}
\usepackage{cases}
\usepackage{graphicx}
%\usepackage{float}
\usepackage{caption}

\renewcommand{\figurename}{Fig.}

\begin{document}

\title{
\bf Fully Automatic Stream Management for Multi-Streamed SSDs \\ Using Program Contexts}

%\numberofauthors{1}
%
%\author{
%	{\rm Taejin Kim$^1$, Sangwook Shane Hahn$^1$, Sungjin Lee$^2$,} \\ 
%	{\rm Jooyoung Hwang$^3$, Jongyoul Lee$^3$, and Jihong Kim$^1$} \\
%	\and
%	$^1$Seoul National University, $^2$DGIST, $^3$Samsung Electronics
%	}


\maketitle
%\thispagestyle{empty}
\pagestyle{empty}
\subsection*{Abstract}
Multi-streamed SSDs
can significantly improve both the performance and lifetime of flash-based SSDs
when their streams are properly managed.  
However, current multi-streamed SSDs have several limitations for their wide adoption.   
Existing stream management techniques are not fully automatic, 
thus requiring manual stream allocation from application developers.  
The number of available streams in multi-streamed SSDs is small, making efficient stream management even more challenging.  
Furthermore, when an SSD is changed with a different number of streams, 
application developers should modify their stream management implementation.
In this paper, we propose a {\it fully-automatic} stream
management approach which effectively overcome the existing limitations of multi-streamed SSDs. 
First, we present  an automatic stream management technique, PCStream, which requires 
no manual coding at all from existing applications.   
PCStream is based on our observation that data lifetimes can be effectively managed
using write program contexts.
By extracting program contexts during runtime, PCStream automates 
the program context to stream mapping using a clustering method.
In order to effectively increase the number of streams, we propose a new type of streams, 
called internal streams, in addition to existing streams that can be considered as external streams.  
Unlike external streams, internal streams are not constrained by the SSD resource budget in 
their implementation so that the number of internal streams are easily increased.   
We use internal streams only for garbage collection.  
When data mapped to the same stream show large differences in their lifetimes, 
PCStream separates the long-lived data of the current stream to an internal stream  
By using GC-only streams, we can easily separate streams with
different lifetimes without affecting the overall performance.    
Our evaluations on real SSDs show that PCStream can reduce the write amplification factor by up to 58\% 
without modifying the application.



\input{introduction}
\input{motivation}
\input{programcontext}
\input{internalstream}
\input{pcstream}
\input{experiment}
\input{relatedwork}
\input{conclusion}


\begin{comment}
\section*{Acknowledgments}

This work was supported by the National Research Foundation of Korea (NRF) 
grant funded by the Korea government (Ministry
of Science and ICT) 
(NRF-2015M3C4A7065645 and NRF-2018R1A2B6006878).
The ICT at Seoul National University
provided research facilities for this study. 
Sungjin Lee was supported by
the NRF grant funded by the Korea government 
(Ministry of Science and ICT) 
(NRF-2017R1E1A1A01077410) and 
the DGIST R\&D Program of the Ministry of 
Science and ICT (18-EE-01).
(Corresponding Author: Jihong Kim)
\end{comment}

\input{reference}

\end{document}
