\newpage
\bibliographystyle{abbrv}
%\bibliography{sigproc}
\begin{thebibliography}{00}

\bibitem{DAC}
M. Chiang, P. Lee, R. and Chang,
Using Data Clustering to Improve Cleaning Performance for Flash Memory,
\textit{Software-Practice \& Experience, vol. 29, no. 3, pp. 267-290}, 1999.

\bibitem{WriteAmplification}
X. Hu, E. Eleftheriou, R. Haas, I. Iliadis, and R. Pletka,
Write Amplification Analysis in Flash-Based Solid State Drives,
In \textit{Proceedings of the ACM International Systems and Storage Conference (SYSTOR)}, 2009

\bibitem{GCGreedy}
W. Bux, and I. Iliadis,
Performance of Greedy Garbage Collection in Flash-Based Solid-State Drives,
\textit{Performance Evaluation, vol. 67, no. 11, pp. 1172-1186}, 2010.

\bibitem{GCVictim}
C. Tsao, Y. Chang, and M. Yang,
Performance Enhancement of Garbage Collection for Flash Storage Devices: 
An Efficient Victim Block Selection Design,
In \textit{Proceedings of the Annual Design Automation Conference (DAC)}, 2013.

\bibitem{GCTTFlash}
S. Yan, H. Li, M. Hao, M. Tong, S. Sundararaman, A. Chien, and H. Gunawi,
Tiny-tail Flash: Near-perfect Elimination of Garbage Collection Tail Latencies in NAND SSDs,
In \textit{Proceedings of the USENIX Conference on File and Storage Technologies (FAST)}, 2017.

\bibitem{HotCold}
J. Hsieh, T. Kuo, and L. Chang,
Efficient Identification of Hot Data for Flash Memory Storage Systems,
\textit{ACM Transactions on Storage, vol. 2, no. 1, pp. 22-40}, 2006.

\bibitem{JiTGC}
S. Hahn, S. Lee, and J. Kim,
To Collect or Not to Collect: Just-in-Time Garbage Collection for High-Performance SSDs with Long Lifetimes,
In \textit{Proceedings of the Design Automation Conference (DAC)}, 2015.

\bibitem{ShadowGC}
J. Cui, Y. Zhang, J. Huang, W. Wu, and J. Yang,
ShadowGC: Cooperative Garbage Collection with Multi-Level Buffer for Performance Improvement 
in NAND flash-based SSDs,
In \textit{Proceedings of the Design, Automation and Test in Europe Conference and Exhibition (DATE)}, 2018.

\bibitem{T10}
SCSI Block Commnads-4 (SBC-4),
\url{http://www.t10.org/cgi-bin/ac.pl?t=f&f=sbc4r15.pdf}.

\bibitem{MultiStream}
J. Kang, J. Hyun, H. Maeng, and S. Cho,
The Multi-streamed Solid-State Drive,
In \textit{Proceedings of the Workshop on Hot Topics in Storage and File Systems (HotStorage)}, 2014.

\bibitem{Level}
F. Yang, D. Dou, S. Chen, M. Hou, J. Kang, and S. Cho,
Optimizing NoSQL DB on Flash: A Case Study of RocksDB,
In \textit{Proceedings of IEEE the International Conference on Scalable Computing
and Communications (ScalCom)}, 2015.

\bibitem{vStream}
H. Yong, K. Jeong, J. Lee, J. Kim,
vStream: Virtual Stream Management for Multi-streamed SSDs,
In \textit{Proceedings of the USENIX Workshop on Hot Topics in Storage
and File Systems (HotStorage)}, 2018.

\bibitem{FStream}
E. Rho, K. Joshi, S. Shin, N. Shetty, J. Hwang, S. Cho. and D. Lee,
FStream: Managing Flash Streams in the File System,
In \textit{Proceedings of the USENIX Conference on File and Storage Technologies (FAST)}, 2018.

\bibitem{AutoStream}
J. Yang, R. Pandurangan, C. Chio, and V. Balakrishnan,
AutoStream: Automatic Stream Management for Multi-streamed SSDs,
In \textit{Proceedings of the ACM International Systems and Storage Conference (SYSTOR)}, 2017.

\bibitem{RocksDB}
Facebook,
\url{https://github.com/facebook/rocksdb}.

\bibitem{Cassandra}
Apache Cassandra,
\url{http://cassandra.apache.org}.


\bibitem{PC}
C. Gniady, A. Butt, and Y. Hu,
Program-Counter-based Pattern Classification in Buffer Caching,
In \textit{Proceedings of the Symposium on Operating Systems Design and Implementation (OSDI)}, 2004.

\bibitem{PC2}
F. Zhou, J. Behren, and E. Brewer,
Amp: Program Context Specific Buffer Caching,
In \textit{Proceedings of USENIX Annual Technical Conference (ATC)}, 2005.

\bibitem{PCHa}
K. Ha, and J. Kim,
A Program Context-Aware Data Separation Technique for Reducing Garbage Collection Overhead in NAND Flash Memory,
In \textit{Proceedings of International Workshop on Storage Network Architecture 
and Parallel I/Os (SNAPI)}, 2011.

\bibitem{kmeans}
J. Hartigan, and M. Wong,
Algorithm as 136: A k-means Clustering Algorithm,
\textit{Journal of the Royal Statistical Society. Series C (Applied Statistics),
vol. 28, no. 1, pp. 100-108}, 1979.

\bibitem{LSM}
P. ONeil, E. Cheng, D. Gawlick, and E. ONeil,
The Log-Structured Merge-Tree (LSM-Tree),
\textit{Acta Informatica, vol. 33, no. 4, pp. 351-385}, 1996.

\bibitem{TRIM}
J. Corbet,
Block Layer Discard Requests,
\url{https://lwn.net/Articles/293658/}.

\bibitem{NVMe}
NVM Express Revision 1.3,
\url{http://nvmexpress.org/wp-content/uploads/NVM_Express_Revision_1.3.pdf}.

\bibitem{TCM}
S. Frank,
Tightly Coupled Multiprocessor System Speeds Memory-Access Times,
\textit{Electronics, vol. 57, no. 1}, 1984.

\bibitem{SQLite}
SQLite,
\url{https://www.sqlite.org/index.html}.


\bibitem{GCC}
R. Stallman, and GCC Developer Community,
Using the GNU Compiler Collection for GCC version 7.3.0,
\url{https://gcc.gnu.org/onlinedocs/gcc-7.3.0/gcc.pdf}.

\bibitem{PM963}
Samsung, Samsung SSD PM963, 
\url{https://www.compuram.de/documents/datasheet/Samsung_PM963-1.pdf}

\bibitem{JNI}
S. Liang,
Java Native Interface: Programmer's Guide and Specification,
1999.

\bibitem{MySQL}
MySQL,
\url{https://www.mysql.com}.

\bibitem{PostgreSQL}
PostgreSQL,
\url{https://www.postgresql.org}.

\bibitem{OpenJDK}
OpenJDK,
\url{http://openjdk.java.net/}.

\bibitem{nvmecli}
NVM-Express user space tooling for Linux,
\url{https://github.com/linux-nvme/nvme-cli}.

\bibitem{YCSB}
B. Cooper, A. Silberstein, E. Tam, R. Ramakrishnan, and R. Sears,
Benchmarking Cloud Serving Systems with YCSB,
In \textit{Proceedings of the ACM Symposium on Cloud Computing (SoCC)}, 2010.

\bibitem{TPCC}
The Transaction Processing Performance Council,
Benchmark C,
\url{http://www.tpc.org/tpcc/default.asp}. 

\bibitem{PCStream} 
T. Kim, S. Hahn, S. Lee, J. Hwang, J. Lee and J. Kim,
PCStream: Automatic Stream Allocation Using Program Contexts,
In \textit{Proceedings of the USENIX Workshop on Hot Topics in Storage
and File Systems (HotStorage)}, 2018.

\bibitem{MonetDB}
MonetDB,
\url{https://www.monetdb.org}.

\bibitem{mmap}
Linux Programmer's Manual,
mmap(2) - map files or devices into memory,
\url{http://man7.org/linux/man-pages/man2/mmap.2.html}.

\end{thebibliography}
